Supporting Information

### 2018-04-21 SupportingInformation.Rmd
temporary solution for ylim with se=NA

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

@@

```{r cause4copula_stat_C_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_C_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SC_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SC_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_G_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=4,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_G_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=4,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SG_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=14,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SG_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=14,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 10000 points are generated but we kept last **500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf)

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 10000 points are generated but we kept last **2500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf)

>>>>

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

@@

```{r cause4copula_stat_C_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_C_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SC_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SC_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_G_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=4,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_G_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=4,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SG_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=14,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SG_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=14,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last **500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf)

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last **2500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf)
